%!TEX root = ../thesis.tex

\chapter{Separating the spectra of faint companions} % Main chapter title
\label{cha:direct_recovery}

Spectral observations of binary systems contain the spectra of both bodies, in proportion to their flux ratio, and Doppler shifted relative to each other due to their orbital motion.
There many different techniques to disentangle the spectra of binary objects.
This chapter focuses on applying a direct subtraction method to near-infrared (\nir{}) spectra of {FGK} stars which have Brown Dwarf (BD) companions, with the goal to isolate the spectrum of the companions.
The data used was obtained with the {CRIRES} instrument in 2012\footnote{Before this thesis began} observed with the purpose to apply the differential technique specifically.
A level of trust was placed in the quality of the observations, which was unfortunately misplaced.
This chapter begins with the motivation for these specific targets and details the observations obtained.
The direct subtraction technique will be presented and its application to the observations will explored.
The limits of the differential technique at low {RV} separations is given by simulation with synthetic spectra.

\input{./chapters/direct_recovery/disentangling_techniques}

\input{./chapters/direct_recovery/motivation}

\input{./chapters/direct_recovery/the_data}

\input{./chapters/direct_recovery/expected_RV}

\input{./chapters/direct_recovery/differential_subtraction}

\input{./chapters/direct_recovery/differential_results}

\input{./chapters/direct_recovery/relative_amplitude}




\section{Orbital Solutions}
\label{sec:orbtial_diagrams}
The insufficient observational spacing becomes clear when the orbits are visualized by plotting the {RV} variation.
\Crefrange{fig:hd4747p89}{fig:hd30501p89} show the {RV} curves for each target observed for this project.
The target stars that have two companions are shown twice, with each companion treated as a single Keplerian (ignoring the presence of the other companion).
For each figure the left hand plot shows the {RV} variation across a full orbit of the companion, while the plot on the right shows the {RV} variation for the 6 month observation window of {Period 89} only.
The solid black line indicates the {RV} of the host star (with scale on the left hand axis), while the blue dashed line shows the {RV} of the companion (with the scale on the right hand axis).
The orange crosses and red stars indicate on the {RV} curves the times at which observations were obtained for each target, for the host and companion respectively.

The first thing that is apparent is the variation of shape of the {RV} curves.
This is normal with the variations in shape arise from the different orbital parameters of each target (provided in \cref{tab:orbitparams}).
In the left hand plots, in which a full orbit is shown, the different shapes are created from the eccentricity, \(e\), and argument of periapsis, \(\omega\).
In the right hand panels, for which a fixed time period is shown, the orbital period of the companion also plays a role.
Specifically the ratio of orbital period to the 6 month observing period determines what fraction (or multiples) of the orbit is displayed.

The {RV} curves of the star and the planet mirror each other about the systems mean velocity, \(\gamma\), with the amplitude scaled by their mass ratio, \(q\) (see \cref{eqn:q_ratio_K2}), and \(\omega\) offset by \(180^\circ\).

All the plots, apart from {HD\,4747}, have more than one observations shown, although it can be difficult to see as there observational spacing is small.

For the companions {HD\,162020}b (\cref{fig:hd162020p89}) and {HD\,168443}b (\cref{fig:hd168443bp89}) their orbital periods are shorter than 6 months, allowing for multiple orbits to occur during {Period 89}.
As such the full amplitude range was available to measure in the observing Period if observations were taken at correct times, at the locations of the extrema.
It should have been possible to obtain observations in which the companion spectra were sufficiently separated for the differential separation technique.
However in reality, the two observations for these two targets were taken immediately after each other, making any differential extremely small.
This is ignoring the fact that the flux ratios (from \cref{tab:estimated_flux_ratios}) for these short period companions are estimated to be very low, meaning they would have been very difficult to detect even if observed at the extrema.

The larger companion {HD\,168443}c in \cref{fig:hd168443cp89} has a longer orbital period, so it appear as straight line in the right hand panel, although the amplitude variation of the companion during {Period 89} is about 8--9\kmps.
Therefore observations taken at the extreme ends of {Period 89} may have provided just enough separation to be suitable for the differential.

For HD\,202206 about 3/4 of the orbit is covered in {Period 89} with a {RV} amplitude of the companion possible of over 40\kmps{}.
Therefore, in this case well separated {RV}s could have been obtained.

For the remaining targets with long periods, it is clear that sufficiently separated {RV}s were not obtained, but also that they were not possible within a single observing period with a {RV} variation less than 6\kmps{} during {Period 89}.
For HD\,30501 the largest time separation between observations obtained is clearly visible in \cref{fig:hd30501p89}.
Unfortunately, this did not result in a large enough companion separation.
Looking at the full period, if the observations had been obtained in the previous period then sufficient separation could have possibly been obtained.

The code used to create orbital plots similar to those shown here is available under the \href{https://github.com/iastro-pt/ObservationTools}{iastro-pt/Observationtools} \emph{Github} repository with documentation available on \href{https://ia-observationtools.readthedocs.io/en/latest/rv.html}{Read the Docs}.


The sampling of points in the orbit reveal that the choice of points was not favourable for the application of the direct subtraction technique.
This was unfortunately discovered after attempting to apply the technique.

\input{chapters/orbital_plots_section}



\subsubsection{Differential scheduling challenges}
\label{subsubsec:differential-schedualing}
This work has revealed that care needs to be taken in planning the observations for the application of the spectral differential technique of faint companions in the future.
Future attempts need to pay attention in particular to: the {\fwhm} of the lines in the region (governed by resolution and wavelength), the estimated companion separation \(\Delta {RV}_2\); and the previous observations from different observing periods, all while and keeping the detector settings consistent.

The original goal for the observations was to obtain two different and ``clearly separated radial-velocities'' for the secondary companion.
However, the program was assigned a low-priority (C, in {ESO} grading) and, possibly due to operational reasons, the original time requirements necessary to secure well separated {RV}s for the companion spectra could not be met.
This meant that all observations were insufficiently separated to extract a differential spectra for the companion.

The long orbital periods of these targets is also a strong contributing factor to the insufficient separations.
Most of the targets observed here have orbital periods much longer than an observing semester (183 days).
An optimal pair of observations (achieved at the extrema) would need to have been obtained from separate observing periods (between 2 months and 19 years apart).
In some cases, even observations taken at the beginning and end of a single observing semester would not be sufficient to achieve a companion separation (depending on the phase and orbital parameters), requiring separate observing periods to even achieve the minimum \(\Delta \rm {RV}\) larger than the line {\fwhm}.
At the time (2012) it was impossible to ask for observation time over several semesters in a regular proposal.

This study demonstrates the importance of proposals for projects that need to be extended over several semesters or years.
In the {ESO} context, this corresponds to ``Monitoring proposals''~\citep[e.g.][pg.~18]{eso_eso_2017}.
Observations of the targets explored here, with long orbital periods in particular, would benefit from the new abilities for multi-period proposals and scheduling systems which allow for tighter scheduling constraints, such as a companion {RV} separation.

For future observations in the context of the differential subtraction technique it is suggested that the best possible orbital solution of the host and companion be used to estimate the companions' {RV} curve during the observing period, with the companion \Mtwosini{} providing an {RV} upper-limit.
Radial velocity constraints are also valid for other studies such as the detection of reflected light from exoplanets~\cite[e.g.]{martins_evidence_2015}.
Knowing the instrumental wavelength and resolution, an observing constraint can be set to avoid taking observations when the companion spectra are insufficiently separated, or the \(\Delta {RV}_2\) < {\fwhm}.
This constraint can be set using the absolute and relative \emph{time-link} constraints available in {ESO}'s {Phase 2 Proposal Preparation} (P2PP) tool.
Additionally, analysing the known orbital solution beforehand to determine {RV} constraints will also help identify the best time to observe, if observations from separate periods will be required or, if an optimally separated companion differential is even feasible.
Again the {P2PP} documentation for this observational proposal could not be obtained to check if these observations had used any of these features, which were available at the time, and set any constraints.


\section{Contrast to other works}

As stated previously the differential technique is not new being analytically formulated for binary star separation in~\citet{ferluga_separating_1997}.
This work tried to extend this to lower contrast ratios, to a hosts with smaller companions.

For lack of high-resolution CRIRES data~\citet{kostogryz_spectral_2013} explored simulations of the differential approach to a {BD} companion of a M-dwarf star, in which the contrast ratio is around 1/50 between 1/200 and were observed at the {RV} extrema.
Their favourable wavelength choice to achieve a good contrast ratio is \emph{K}-band, as done in work, however they chose the \ce{CO} line region (\(\sim2310\)\nm{}) where there is several narrow spectral lines.
One thing explored in~\citet{kostogryz_spectral_2013} that is not considered here is the effect of rotational broadening on the mass determination, finding that it should be possible to determine the mass of a slowly rotating companion, but a fast rotating companion is more difficult.

The limitations with regards to the {RV} separation between spectral components has also been observed in other works.
Similarly to the companion-companion {RV} separation focused on here, \citet{kolbl_detection_2015} find a limitation of \(\sim 10\)\kmps{} {RV} separation required between the host and the companion.
This is because if lines of the host and companion are blended, it is likely the companion spectra will be fitted, or incorporated into the hosts spectra, making it difficult to accurately detect the companions lines a similar {RV}.
The {RV} difference between the host an companion is given in the last column of \cref{tab:observations} as \Rvtwo{}.
It can be seen {HD~4747}, {HD~202206}, and {HD~218447} do not exceed this 10\kmps{} separation with the obtained observations.


\section{Direct recovery in the \mir{}}
It was investigated if this differential technique could be extended into the mid-infrared {\mir{}} domain.
There were two reasons for this: to develop experience with the {\mir{}} domain where the contrast ratios are higher, and due to the lack of high-resolution \nir{} spectrographs available at the time (see \cref{subsec:new_generation}).

{VISIR} is a \mir{} spectrograph on the {VLT}, offering diffraction-limited imaging at high sensitivity in three mid-infrared (\mir) atmospheric windows: the \emph{M}-band at 5\um{}, the \emph{N}-band between 8--13\um{} and the \emph{Q}-band between 17--20\um{}, respectively.
The use of {VISIR} to detect the spectra of Brown Dwarf companions in the {\mir{}} was briefly explored.
The candidate selected as the best target to investigate was {HD\,219828} which has a hot-Neptune (\Mtwosini{}=21\Mearth)~\citep{melo_new_2007} and a recently discovered super Jupiter (\Mtwosini{}=15.1\,\Mjup) on a long period (13 yr) eccentric orbit (e=0.81)\citep{santos_extreme_2016}.

Based on the spectra of a cool brown dwarfs in the \mir{}, and the detector configuration available at the time, the best option for the observations was the low resolution mode covering the wavelength region 8--13\um{}.
This wavelength region would have encompassed the \ce{NH4} signature at 10.5\um{} and the edge of a \ce{CH4} band at 7.7\um{}, both large features in the {BD} \mir{} spectrum.

After performing flux ratio calculations between the host and companion using the~\citet{baraffe_evolutionary_2003} models (see \cref{subsec:compaion_flux_ratio}) and considering the performance of the {VISIR} instrument and the exposure time calculator it was determined that observations with {VISIR} to achieve a \snr{} of 100 were infeasible, requiring 1000's of hours of observing time to achieve the necessary signal-to-noise level to separate the companion from a blended spectra.
For a different target, {HD\,189733} it was calculated that with an exposure time 2 hours the \snr{} of the host and companion would be 85 and 4 respectively, using the low resolution spectroscopy mode.
As such the direct separation approach was not explored further in the \mir{}.


\section{Summary}
This chapter presented the observations that were gathered having in mind the application of a differential subtraction method to recover the spectra of the faint {BD} companions.
Due to the poorly separated observation times relative to the long orbital periods, the differential subtraction method presented in \cref{sec:direct-subtraction} was revealed to be inappropriate for these observations as the {RV} separation of the companion spectra between observations is significantly smaller than the width of individual spectral lines.
The small separation of the companion causes the lines of the companion to also mutually cancel, severely reducing the residual signal to well below the available noise level.
The requirement of well separated {RV}s for the companion spectra was clearly stated in the original proposal but was not satisfied by the observations, however the very large orbital periods of some of the targets would not produce a sufficient {RV} signal during one semester was possibly and oversight during the proposal stage.
In the following chapter a different technique will be explored in the attempt to extract details of the companion from these observations which were insufficient to apply the differential.
