%!TEX root = ../thesis.tex

\chapter{Introduction}\label{cha:introduction}

\section{Towards the characterization of exoplanets}

The field of exoplanetary science is rapidly accelerating.
Large scientific and instrumental investments have been undertaken, with the ultimate goal of detecting and characterizing an Earth-like planet that has the potential for life (as we know it).
Since the very first exoplanet detection around a Sun-like star~\citep{mayor_jupitermass_1995} the number of confirmed exoplanets has grown to over 3872 with another 2898 candidates awaiting confirmation as of January~2019\footnote{\href{https://exoplanets.nasa.gov/}{\url{https://exoplanets.nasa.gov}}.}.
A planet transitions from a ``candidate'' to ``confirmed'' when the probability of false positives is very low, usually achieved using advanced analysis techniques and/or complementary measurements from other detection methods.
However, simply detecting the presence of exoplanets is not nearly enough to satisfy our quest for knowledge.
There is an exorbitant amount of insight to be gained through the full characterization of these known exoplanets, such as: density, composition, internal structure, atmosphere properties, and surface temperature.

When a new extra-solar planet is suspected, follow-up observation and analysis is required to confirm its existence, and its properties.
In particular for the highly sought after Earth-twin, a full characterization is required to determine their habitability.
Notability, here have been several small planets, which have had early claims of Earth-twin status, later determined to be false (or fall below a 99\% probability level) after follow up investigation~\citep[e.g.][]{mullally_kepler_2018,burke_reevaluating_2019}, and the presence of some exoplanets have been heavily debated in literature such as {Gliese~581g}~\citep{vogt_lickcarnegie_2010, gregory_bayesian_2011,robertson_stellar_2014}.
Detecting and analysing exoplanet atmospheres aid in the characterization of exoplanets by allowing their temperature, atmospheric structure, the presence of any scattering aerosols, and the chemical composition to be determined~\citep[e.g.][and references therein]{kreidberg_exoplanet_2018}.
%\todo{references here would be nice}.%exoplanet handbook is a cop-out due to time
All providing clues towards a full exoplanet characterization.

There are several new developments for detecting and characterisation of new exoplanetary systems. For instance, the new space-based transit missions such as {TESS}, {PLATO} and {CHEOPS}.
One of the more promising ground-based approaches is high-resolution near-infrared (\nir{}) spectroscopy.
Several new \nir{} spectrographs are in development~\citep[e.g.][]{wright_third_2017} primarily to detect and characterize exoplanets around cooler {M-dwarf} stars. The \nir{} wavelengths are closer to the peak emissions of cooler stars and exoplanets, while the smaller mass and radius of {M-dwarfs} allow exoplanets to induce larger relative signals that are relatively easier to detect.

In this chapter the common exoplanet and atmospheric detection methods will be introduced, followed by some exoplanet property distributions and the motivation for the work performed in this thesis.

\input{chapters/introduction/detection_methods}

\input{chapters/introduction/atmospheres}

\input{chapters/introduction/planet_bd_formation}

\input{chapters/introduction/motivation}

%\todo{Pedro: I would only note that you can provide a more detailed description on the importance of determining {RV} information content measurement (at the very end of the chapter)}

%\todo{Nuno: I just think it would be good if you could make the bridge to Brown-Dwarfs and to NIR spectroscopy a bit stronger. Some of the comments and suggestions go in that direction. But since this is an overall suggestion, its not very easy to find the best way through. The general impression one has when reading the introduction is that the thesis is about planets. But then one realizes it is not. But that comes late.}
