%!TEX root = ../thesis.tex
% NIR-information

\chapter{Information content in the \nir{}}
\label{cha:nir_content}

The work presented in this chapter focuses on calculating and analysing the information content of stellar spectra, specifically the radial velocity {RV} precision of M-dwarf spectra in the \nir{}. 
M-dwarfs are a source of focus in the community with several new instruments dedicated specifically to detecting planet around M-dwarfs \citep[e.g.][among others]{quirrenbach_carmenes_2014, bouchy_nearinfrared_2017, artigau_spirou_2014}.
The fundamental radial velocity precision of {M-dwarf} spectra attainable at different wavelength regions calculated in~\citet{figueira_radial_2016} was used to inform some design choices of two \nir{} spectrographs, {SPIRou} and {NIRPS}.
Understanding the underlying precision of different spectral types can also allow {RV} surveys to adjust the focus of the target selection, or optimize the exposure time of different spectral types.
This can help in detecting the presence of ``habitable Earth-like'' planets around {M-dwarfs} which have become a prime target with the recent \nir{} spectrographs.

The purpose of the work presented in this chapter is to extend the work of~\citet{figueira_radial_2016}, computing the theoretical {RV} precision of synthetic stellar spectra over a wider range of situations.
A investigation into the effect of \Logg{} and \feh{} on precision is performed and a preliminary comparison of {RV} precision of the recently observed \nir{} {M-dwarf} spectra from {CARMENES} library and their synthetic counterparts is given.
This is to test how the {RV} precision of synthetic models compares to reality.
New computations of the {RV} precision of synthetic spectral libraries are also given, which were provided for exposure time calculators of {NIRPS} and {SPIRou}.


\section{Overview}
\label{sec:precision_overview}
The pursuit of detecting exoplanets, especially ``habitable'' and ``Earth-like'' planets, requires state-of-the-art instrumentation with high precision.
Several new high-resolution \nir{} spectrographs are becoming available now and in the near future, not limited to {CARMENES}, {NIRPS}, {SPIRou} and {CRIRES+} (see \cref{subsec:new_generation}).
One science objective common to all four instruments is the detection of small mass planets around {M-dwarf} stars utilizing the radial velocity technique, an objective strived for in the literature~\citep[e.g.][]{reiners_detecting_2010, rodler_detecting_2011, plavchan_radial_2015}.
As the {RV} amplitude is \(\kone\propto {P}^{-{1/2}}{\mone}^{-2/3}\) (\cref{eqn:k_relation}), the induced {RV} wobble from a similarly massive exoplanet is larger around an M-dwarf star, making the {RV} signal from lower mass exoplanets easier to detect.
Also the cooler {M-dwarfs} have habitable zones closer to the star, at shorter orbital periods, that again have a stronger {RV} amplitude making it easier to detect small mass planets in the habitable zone of {M-Dwarfs}.

To calculate and predict the information content attainable from {M-dwarfs} in the \nir{,}~\citet{figueira_radial_2016} utilized the {PHOENIX-ACES} library of synthetic spectra.
This helped at the early stages of instrument design by identifying the wavelength regions with the best {RV} precision, but can also help in the planning of observations, by understanding how the precision changes with spectral type and observed {\snr{}}.
However, the synthetic spectra do not quite match reality and a comparison between theoretical and observed is needed.
\citet{artigau_optical_2018} recently compared optical ({HARPS}, {ESpaDOnS}) and \nir{} ({CRIRES}) archival spectra of the {M-dwarf}, Barnard's Star, to synthetic spectra.
They found that state-of-the-art atmosphere models over-predict the {RV} content \emph{Y}- and \emph{J}-band {RV} by more than a factor of \(\sim\)2, while under-predicting the \emph{H}- and \emph{K}-band content by half.
A similar comparison will be made in this work to {CARMENES} spectra.

Recent results regarding the measured performance of the {CARMENES} survey~\citep{reiners_carmenes_2018,quirrenbach_carmenes_2018} find that the {RV} in the \nir{} is worse than the pre-survey predictions.
Precisions of 1--2\mps{} have been achieved in the optical but only 5--10\mps{} in the \nir{}.
However, comparing {RV} precision in different wavelength bands~\citet{quirrenbach_carmenes_2018} found a ``sweet spot'' around 0.7--0.8\um{} with deep \ce{TiO} bands providing rich {RV} information in mid-M dwarfs.

The number of papers on this thematic, the number of open questions, and the impact on the design of instrumentation, particularly in the \nir{}, show that this is an important topic as of today.
  

\input{chapters/information_content/photon_noise_precision}


\input{chapters/information_content/synthetic_precision}


\input{chapters/information_content/eniric_software}


\input{chapters/information_content/eniric_results}


\input{chapters/information_content/carmenes_application}


\section{Summary}
Significant advancements in the \eniric{} software have been made to expand and simplify the computation of synthetic {RV} precision.
This software has been used to begin exploring the effect of \Logg{} and \feh{} on the spectral prevision of M-dwarfs, as well as comparing the RV precision of synthetic spectra to observed M-dwarf spectra from {CARMENES}.
Open to the community, it is available to aid in {RV} precision calculations.
