%!TEX root = ../../thesis.tex

\chapter{{RV} Precision Tables} % Main appendix title
\label{appendix:nir_prec_amendment}
The updated relative {RV} precision ($\sigma_{RV}$ or $dV_{\rms}$) results attainable from \nir{} spectra are presented in the following tables.
\cref{tab:rv_aces_btsettl} shows the precision results for the same M-dwarfs analysed in~\citet{figueira_radial_2016}.
That is stellar temperatures 3900, 3500, 2800, 2600\K{} corresponding to spectral types {M0}, {M3}, {M6}, {M9} respectively, \Logg{}=4.5 and \feh{}=0.0.
The rotation applied are \Vsini{}=1, 5, 10\kmps{} and instrumental profiles with \(R\)=60\,000, 80\,000, 100\,000.

Columns 2--4 contain the {RV} precision calculated using {PHOENIX-ACES} spectra, as done in~\citet{figueira_radial_2016}.
These values differ from two effects.
There is small difference in Conditions~\#1 and \#3 from the change in numerical differentiation implemented (see \cref{sec:numerical_gradient}).
The values for Condition 2 however, are completely different due to the implementation error in the telluric masking discovered (see \cref{subsec:condition_two_bug}).

In columns 5--7 are the same {RV} precision calculation but using the {BT-Settl} spectral library instead (with same spectral parameters), a recent addition in \eniric{}.

The {PHOENIX-ACES} {RV} precisions in \cref{tab:rv_aces_btsettl} can be created with \eniric{} using the following shell incantation (after installation and configuration):
\begin{lstlisting}[language={bash},caption={Command line incantation to calculate the {PHOENIX-ACES} {RV} precisions; with comments.},label={lst:commandline_incantation}]
    phoenix_precision.py -t 3900 3500 2800 2600 \   # Temperature
                         -l 4.5 -m 0.5 \            # Logg and Metalicity
                         -r 60000 80000 100000 \    # Resolutions
                         -v 1.0 5.0 10.0 \          # Rotational velocities
                         -b Z Y J H K \             # Wavelength bands
                         --snr 100 \                # Relative SNR
                         --ref_band J               # SNR reference band
                         --model aces               # Spectral model
\end{lstlisting}

\Eniric{} was also used to calculate {RV} precision for the {NIRPS} and {SPIRou}.
For {SPIRou} the requested precisions were provided with the \snr{} relative to the centre of each individual band.
The values are provided in \cref{tab:spirou_precisions} and can be generated with the following code; note the change in the `ref\_band' parameter.

\begin{lstlisting}[language={bash},caption={Shell incantation for the {SPIRou} {ETC} {RV} precisions.},label={lst:spirou_incantation}]
phoenix_precision.py -t 3900 3500 2800 2600 -l 4.5, -m 0.5 \
-r 60000 80000 100000 -v 1.0 5.0 10.0 -b Z Y J H K     \
--snr 100 --ref_band self
\end{lstlisting}

Changing the reference band for the \snr{} scaling increases and decreases the precision in different bands due to the shape of the spectral profile.
Comparing the precision values between \cref{tab:rv_aces_btsettl} and \cref{tab:spirou_precisions}, it has the effect of decreasing the $\sigma_{RV}$ (increasing precision) in the \emph{H}- and \emph{K}-bands while increasing the $\sigma_{RV}$ (decreasing precision) in the \emph{Z}- and \emph{Y}-bands.
The {RV} precision for the \emph{J}-band remains unchanged, so is not included in \cref{tab:spirou_precisions}.


For the {NIRPS} spectrograph, {RV} precisions with an instrumental resolution of 75\,000 was requested to match the {NIRPS} instrument, and provided relative to the \emph{J}- and \emph{H}-bands.
The results for the {NIRPS} precision relative to the \emph{J}-band are given in \cref{tab:nirps_precisions}, and can be reproduced with the following code.

\begin{lstlisting}[language={bash},caption={Shell incantation for the {NIRPS} {ETC} {RV} precisions.},label={lst:nirps_incantation}]
    phoenix_precision.py -t 3900 3500 2800 2600 -l 4.5, -m 0.5  \
        -r 60000 75000 80000 100000 -v 1.0 5.0 10.0             \
        -b Z Y J H K --snr 100 --ref_band J                     \
\end{lstlisting}


\input{tables/appendices/precisions_aces_btsettl_table.tex}

\input{tables/appendices/precisions_spirou_table.tex}

\input{tables/appendices/precisions_nirps_table.tex}
